comgen-outline

### 2017-06-27 paper/comgen-paper.Rmd
edits to model section; up to predictions

Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

# The Bayesian Framework for Generalizations

Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
The linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
We call this kind of statement a *particular*.

```{r table-generalization, results="asis"}
df.tab <- data.frame(
  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
  "Generalization over" = c("Category", "Event", "Cause"),
  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
) #%>% xtable(., 
 #        caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
  #       label = c("tab:genpart"))

apa_table(df.tab, 
          caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
          escape = TRUE, small = TRUE
)

#print(df.tab,  type = "latex", tabular.environment = "tabularx", width = "\\textwidth",  include.rownames = FALSE, comment = F)
```

Particular statements can be made about objects, events, and causes.
We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
<!-- In the study of categories and properties, $x$ is an object. -->
For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
<!-- In this case, $x$ is a instance of an agent. -->
Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$, known as causal power: $h = P(x \in e \mid x \in c)$.
Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the friendliness of dogs.

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent, which is predicted assuming the data-generating process (i.e., the likelihood function) is another agent [@Goodman2009].

@@

# Communicating Generalizations with a Formal Model

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

@@

These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.

The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which was empirically corroborated [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relations can also be expressed such as *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
How do we make sense of this panoply of conditions?
Is there some more general, unified principle that explains what makes generic statements true or false?

Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
The basic currency of inference in these models is probability.
In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:

@@

$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?
We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
We assume this prior is uninformed: $P(\theta) = \text{Uniform}(0, 1)$.

@@

Equation \ref{eq:L0} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.

@@

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
The fixed threshold model rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
If the threshold $\theta$  is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold $\theta$  takes on lower and lower values, more and more $h$ probabilities would surpass it.
When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

In this paper, we are interested in explaining the variable endorsements of generalizations based on some known or believed probability $h$.
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).
\begin{equation} 
S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
\label{eq:S1}
\end{equation}

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

\begin{equation*}
\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
1 &\text{for all h}\ 
\end{cases}
\end{equation*}

Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[
A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate.
Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind. 
In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution: 
$U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
]

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
This *simple but underspecified* hypothesis defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix A.

>>>>

Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

# A Formal View of Generalization

Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
This is faciliated through the use of labeling; the linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
We call this latter kind of statement a *particular*.

```{r table-generalization, results="asis"}
df.tab <- data.frame(
  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
  "Generalization over" = c("Category", "Event", "Cause"),
  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
) %>% xtable(.,
         caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
        label = c("tab:genpart"))

# apa_table(df.tab, 
#           caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
#           escape = TRUE, small = TRUE
# )

print(df.tab, type = "latex", 
      tabular.environment = "tabularx", width = "\\textwidth",
      scalebox='0.75',
      include.rownames = FALSE, comment = F)
```

Particular statements can be made about objects, events, and causes (e.g., "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind.").
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category (e.g., being friendly among dogs), we can describe this inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
<!-- In the study of categories and properties, $x$ is an object. -->
For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
<!-- In this case, $x$ is a instance of an agent. -->
Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency of some instance in a category.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
Observations that are generated by an intentional agent can similar lead to subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].

@@

# Formalizing Generalizations in Language

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

@@

These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
**Conceptual accounts** of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as a special way of expressing mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.

The *generics as default* view argues that general cognitive principles explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which was empirically corroborated [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relationships can also be expressed (e.g., *Barns are red*; *Ravens are bigger than toasters*) which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
This diversity is interested, but what is common across generics?
Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false?

We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction.
We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities. 
Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
Thee basic currency of inference in these models is probability.
In generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
<!-- In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability. -->
<!-- If that's true, a simple, semantic theory  -->

@@

$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?

To answer this, we draw a metaphor to Bayesian statistics and data analysis.
When there is a latent parameter the Bayesian scientist doesn't know much about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$ (in the form of a prior distribution $P(\theta)$) and infers $\theta$ in context (i.e., after having heard the utterance).
Though it's possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across context and is completely uninformed: $P(\theta) = \text{Uniform}(0, 1)$.

@@

Equation \ref{eq:L0} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances described above.

@@

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threshold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
The fixed threshold model rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind the model's behavior can be gleaned by imagining what the listener $L$ would believe with different thresholds and averaging over those possibilities.
If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
If the threshold $\theta$  is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold $\theta$  takes on lower and lower values, more and more $h$ probabilities would surpass it.
When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
When the listener averages over these possibilities, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

In this paper, we are interested in explaining the variable endorsements of generalizations (e.g., *Birds lay eggs* is good; *Birds are female* is not) based on some known or believed probability $h$ (e.g., only female birds lay eggs).^[
A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that she is trying to communicate.
Rather, the speaker may have a belief distribution over $h$ for the category. $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution: 
$S_{belief}(u \mid k) \propto \exp{(\lambda = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
]
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).
\begin{equation} 
S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
\label{eq:S1}
\end{equation}

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
Since the speaker $S$ doesn't know the threshold $\theta$, she must integrate over the likely values that the listener will infer.

The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the utterance vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

\begin{equation*}
\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
1 &\text{for all h}
\end{cases}
\end{equation*}

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
This *simple but underspecified* hypothesis defines a *class* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix.
